A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2024-12-15 manuscript/manuscript.qmd
added example table for agreement metrics

library(here)
library(dplyr)
library(knitr)
library(gt)
library(readxl)
library(fs)
library(webshot2)
library(tibble)
library(ggplot2)
library(cowplot)
library(mice)
library(MatchThem)
library(cobalt)
library(gtExtras)
```

@@

To formally compare treatment effects between RCTs and their respective emulations, we will adapt the approach of the RCT-DUPLICATE project.[@franklin2020nonrandomized; @wang2023emulation] That is, for the primary endpoint of interest (HR and corresponding 95% confidence intervals), we will derive two qualitative agreement metrics (regulatory agreement, estimate agreement) and one quantitative agreement based on the SMD.

@@

@@

```{r}
#| label: fig-metrics
#| fig-cap: "Visualization of agreement metrics example."
#| fig-widh: 4
#| fig-height: 7

data <- tribble(
  ~group, ~estimate, ~lower, ~upper,
  "RCT", 0.75, 0.61, 0.91,
  "RWE", 0.80, 0.51, 1.1
  )

smd <- smd_agreement(
  rct_estimate = data |> filter(group == "RCT") |> pull(estimate),
  rct_lower = data |> filter(group == "RCT") |> pull(lower),
  rct_upper = data |> filter(group == "RCT") |> pull(upper),
  rwe_estimate = data |> filter(group == "RWE") |> pull(estimate),
  rwe_lower = data |> filter(group == "RWE") |> pull(lower),
  rwe_upper = data |> filter(group == "RWE") |> pull(upper)
  )

data |> 
  gt() |> 
  gt_plt_conf_int(
    column = estimate, 
    ci_columns = c(lower, upper),
    ref_line = 1,
    palette = c("red", "lightgrey", "black", "red")
    ) |> 
  cols_hide(c(lower, upper)) |> 
  # add agreement metrics
  cols_add(
    metric = c(md("Regulatory agreement: <br><br> Estimate agreement:"), "SMD:"),
    results = c(md("No <br><br> Yes"), ifelse(abs(smd) < 1.96, "Yes", "No"))
    ) |> 
  tab_options(
    table_body.hlines.width = px(0)
  ) |> 
  cols_label(
    group = "",
    estimate = "HR (95% CI)",
    metric = "Agreement metrics",
    results = ""
    ) |> 
  fmt_markdown() |> 
  tab_style(
    style = cell_text(align = "center", v_align = "middle"),
    locations = cells_column_labels()
    ) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
    )
```

>>>>

library(here)
library(dplyr)
library(knitr)
library(gt)
library(readxl)
library(fs)
library(webshot2)
library(tibble)
library(ggplot2)
library(cowplot)
library(mice)
library(MatchThem)
library(cobalt)
library(gtExtras)
library(glue)
library(tidyr)
```

@@

To formally compare treatment effects between RCTs and their respective emulations, we will adapt the approach of the RCT-DUPLICATE project.[@franklin2020nonrandomized; @wang2023emulation] That is, for the primary endpoint of interest (HR and corresponding 95% confidence intervals), we will derive two qualitative agreement metrics (regulatory agreement, estimate agreement) and one quantitative agreement based on the SMD (examples are illustrated @tbl-metrics).

@@

```{r}
#| label: tbl-metrics
#| tbl-cap: "Visualization of agreement metrics example."

data <- tribble(
  ~trial, ~group, ~estimate, ~lower, ~upper,
  "Trial 1", "RCT", 0.75, 0.61, 0.91,
  "Trial 1", "RWE", 0.80, 0.51, 1.1,
  "Trial 2", "RCT", 0.62, 0.51, 0.71,
  "Trial 2", "RWE", 0.65, 0.55, 0.69,
  "Trial 3", "RCT", 0.71, 0.67, 0.80,
  "Trial 3", "RWE", 0.51, 0.41, 0.61,
  "Trial 4", "RCT", 0.90, 0.81, 0.99,
  "Trial 4", "RWE", 1.2, 1.09, 1.34,
  ) |> 
  pivot_wider(names_from = group, values_from = c(estimate, lower, upper)) |> 
  mutate(
    smd_value = smd_agreement(
      rct_estimate = estimate_RCT, 
      rct_lower = lower_RCT, 
      rct_upper = upper_RCT,
      rwe_estimate = estimate_RWE,
      rwe_lower = lower_RWE, 
      rwe_upper = upper_RWE
      )
    ) |> 
  mutate(
    regulatory = ifelse(
      # superiority
      estimate_RCT < 1 & upper_RCT < 1 & estimate_RWE < 1 & upper_RWE < 1 |
        # non-inferiority
        estimate_RCT < 1 & upper_RCT >= 1 & estimate_RWE < 1 & upper_RWE >= 1 |
        # inferiority (made up)
        estimate_RCT >= 1 & lower_RCT >= 1 & estimate_RWE >= 1 & upper_RWE >= 1,
      "Yes", "No"
      ),
    estimate = ifelse(
      estimate_RWE >= lower_RCT & estimate_RWE <= upper_RCT, "Yes", "No"
      ),
    smd = ifelse(
      abs(smd_value) < 1.96, "Yes", "No"
      )
    )

tbl_metrics <- data |> 
  mutate(across(where(is.numeric), function(x) format(x, digits = 2, nsmall = 2))) |> 
  mutate(
    RCT = glue("{estimate_RCT} ({lower_RCT} - {upper_RCT})"),
    RWE = glue("{estimate_RWE} ({lower_RWE} - {upper_RWE})"),
    smd = glue("{smd} ({smd_value})")
  ) |> 
  select(trial, RCT, RWE, regulatory, estimate, smd) |> 
  gt() |> 
  tab_spanner(
    label = "HR (95% CI)",
    columns = c(RCT, RWE)
  ) |> 
  cols_label(
    trial = "Trial",
    regulatory = md("Regulatory <br> agreement"),
    estimate = md("Estimate <br> agreement"),
    smd = "SMD"
    ) |> 
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
    ) |> 
    tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_spanners()
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), # Pink for "Inactive"
    locations = cells_body(
      columns = regulatory,
      rows = regulatory == "Yes"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), # Pink for "Inactive"
    locations = cells_body(
      columns = regulatory,
      rows = regulatory == "No"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), # Pink for "Inactive"
    locations = cells_body(
      columns = estimate,
      rows = estimate == "Yes"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), # Pink for "Inactive"
    locations = cells_body(
      columns = estimate,
      rows = estimate == "No"
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkgreen"), # Pink for "Inactive"
    locations = cells_body(
      columns = smd,
      rows = grepl("^Yes", smd)
      )
    ) |> 
  tab_style(
    style = cell_text(color = "darkred"), # Pink for "Inactive"
    locations = cells_body(
      columns = smd,
      rows = estimate == "No"
      )
    )

# save table as .docx document
tbl_metrics |> 
   gtsave(
    filename = here("manuscript", "Table_3_agreement_metrics.docx")
    )

# save image to display within manuscript document
suppressMessages(tbl_metrics |> 
  gtsave(
    filename = here("tables", "Table_3_agreement_metrics.png"),
    expand = 10, # amount of whitespace,
    zoom = 5 # higher resolution
    ))

include_graphics(path = here("tables", "Table_3_agreement_metrics.png"))
```

@@
